AAAI Press Formatting Instructions \\for Authors Using \LaTeX{} --- A Guide

### 2021-09-18 publications/iaai21/dora_outlier_detection_iaai.tex
added DES info to tab:datasets
added small paragraph for DES results

    \hline
    Astrophysics &   &   &   \\
    Earth & 6,757 & 37 & 76  \\
    Planetary & 992 &  9 & 49 \\
    F-MNIST & 60,000 & 1,000 & 1,000  \\
    \hline
  \end{tabular}
\end{table}

@@

\todo{Umaa: add results for astro use case.}

>>>>

    \hline
    Astrophysics & 100,000   &  25,339 &  74,661 \\
    Earth & 6,757 & 37 & 76  \\
    Planetary & 992 &  9 & 49 \\
    F-MNIST & 60,000 & 1,000 & 1,000  \\
    \hline
  \end{tabular}
\end{table}

@@

For the astrophysics dataset (Figure~\ref{fig:des_results}, DEMUD was omitted due to computational time 
and LRX was omitted as it applies only to image data.  Of the remaining methods, 
PCA achieved the highest precision, following by RX.  Negative sampling 
performs well initially before its performance drops off.  The PAE finds the most outliers 
overall.
